Download data

### 2023-12-05 scripts/download_dependent_variables.Rmd
adding usda codes manual review

```{r import and clean target species}
targets <- read.csv('../data/raw/2024sos_species.csv', na.strings = "") %>% 
  filter(!species %in% c('tridentata', 'millefolium', 'dioica', 'negundo')) # purshia, artemisia, and larrea !

target_taxa <- unite(targets, 'taxon', genus:infraspecies, na.rm = T, sep = ' ') %>% 
  pull(taxon) %>% 
  unique() # 293 species.

@@

## we will add on USDA codes so we can interface with AIM data.

>>>>

```{r import and clean target species}
targets <- read.csv('../data/raw/2024sos_species.csv', na.strings = "") %>% 
  filter(!species %in% c('tridentata', 'millefolium', 'dioica', 'negundo')) %>%  # purshia,
  unite('taxon', genus:infraspecies, na.rm = T, sep = ' ') # artemisia, and larrea !

target_taxa <- targets %>% 
  pull(taxon) %>% 
  unique() # 293 species.

@@

## we will add on USDA codes so we can interface with AIM data. 
symbols <- read.csv('../data/raw/USDA_PLANTS.csv') %>% 
  right_join(., targets, by = c('' = 'taxon'))
